Modelling the gas kinematics of an atypical Lyman-$\alpha$ emitting compact dwarf galaxy

### 2017-03-13 paper/letter.tex
refs caption

\begin{figure*}
\begin{center}
\includegraphics[width=0.55\textwidth]{CLARA-TOL-main.pdf}
\caption{Broad, single peaked and symmetric Ly-$\alpha$ emission of \tol.
  Dots correspond to the observational data. The line shows the results
of our best model from a full radiative transfer simulation both for
the rotation and multiphase models.} 
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.6\textwidth]{vinf_cl.pdf}
  \includegraphics[width=0.6\textwidth]{P_cl.pdf}
  \includegraphics[width=0.6\textwidth]{sigma_cl.pdf}
\caption{Results from the multiphase
  model.
  The left column corresponds to the parameter's integrated distributions for
  models with the lowest $\chi^2$ values (dotted line) compared against the
  parameter's integrated distributions (continous line) used as a prior.
  These are the only three parameters that show a significant statistical difference from
  the prior distributions, for all the other eleven parameters we
  cannot find any significant difference.
  \label{multiphaseresults}
}  
\end{center}
\end{figure*}

@@

We explore flat priors on four parameters: $200<V_{\rm
  max}/\mathrm{km\ s}^{-1} <600$,   $6.0<\log_{10}\tau<9.0$,
$4.0<\log_{10} T/10^4\mathrm{K}< 4.5$ and $0<\theta<90$ using $500$
steps with $24$ walkers for a total of $12000$ points in the chain.
We estimate the parameter values from the 16th, 50th and 84th
percentiles.

@@

A first possibility to explain a dynamical mass of $10^{9} M_{\odot}$
in a sphere of 2.25 kpc in radius, could be a dark matter halo of at
least $10^{12}$ M$_{\odot}$ in mass \citep{2011ApJ...726..108T}, which
leaves open the question as to why  \tol\ is not more similar to the
Milky Way galaxy as it would be hosted by a dark matter halo of similar
mass.

@@

Another observational test includes the measurement of the
\lya\ ionizing continuum escape fraction.
In the rotational model this fraction should be zero, while
the multiphase model predicts that averaging over all sightlines
it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
variations depending on viewing angle \citep{2014MNRAS.444.1095G}.

@@

\section*{Acknowledgments}
We thank J. M. Mas-Hesse for providing us with \tol's observational
\lya\ data \citep{Mas-Hesse09} in electronic format. This data was
used to prepare Figure 1.

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.55\textwidth]{CLARA-TOL-main.pdf}
\caption{Broad, single peaked and symmetric Ly-$\alpha$ emission of \tol.
  Dots correspond to the observational data. The line shows the results
of our best model from a full radiative transfer simulation both for
the rotation and multiphase models.
The observational points corresponds to the data as shown in
\citep{mashesse03}.}   
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.6\textwidth]{vinf_cl.pdf}
  \includegraphics[width=0.6\textwidth]{P_cl.pdf}
  \includegraphics[width=0.6\textwidth]{sigma_cl.pdf}
\caption{Results from the multiphase
  model.
  The left column corresponds to the parameter's integrated distributions for
  models with the lowest $\chi^2$ values (dotted line) compared against the
  parameter's integrated distributions (continous line) used as a prior.
  These are the only three parameters that show a significant statistical difference from
  the prior distributions, for all the other eleven parameters we
  cannot find any significant difference.
  The right column shows a scatter plot of $\chi^2/1000$
  and its corresponding physical parameters.
  Only the  25 models with the lowest $\chi^2$ are included.
  \label{multiphaseresults}
}  
\end{center}
\end{figure*}

@@

We explore flat priors on four parameters: $200<V_{\rm
  max}/\mathrm{km\ s}^{-1} <600$,   $6.0<\log_{10}\tau<9.0$,
$4.0<\log_{10} T/10^4\mathrm{K}< 4.5$ and $0<\theta<90$ using $500$
steps with $24$ walkers for a total of $12000$ points in the chain.
Previous exploratory work shows that it is impossible to fit the
observed line outside thsese priors.
Finally, we estimate the parameter values from the 16th, 50th and 84th
percentiles.

@@

A first possibility to explain a dynamical mass of $10^{9} M_{\odot}$
in a sphere of 2.25 kpc in radius, could be a dark matter halo of at
least $10^{12}$ M$_{\odot}$ in mass \citep{2011ApJ...726..108T}.
This estimate is based on computing the integrated mass profile of a
spherical dark matter halo with a Navarro-Frenk-White profile with its
concentration following the \emph{median} mass-concentration
relationship found in the Bolshoi simulation
\citep{2012MNRAS.423.3018P}. 
This estimate leaves open the question as to why  \tol\ is not more
similar to the Milky Way galaxy as it would be hosted by a dark matter
halo of similar mass.

@@

Another observational test includes the measurement of the
\lya\ ionizing continuum escape fraction.
In the rotational model this fraction should be zero, while
the multiphase model predicts that averaging over all sightlines
it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
variations depending on viewing angle \citep{Gronke2016}.

@@

\section*{Acknowledgments}
We thank J. M. Mas-Hesse for providing us with \tol's observational
\lya\ data \citep{mashesse03} in electronic format. This data was
used to prepare Figure 1.
